Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
small modification

	\subsection{LSTM Model}
	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling. More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
	\begin{equation}
	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
	\begin{equation}
	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
	\end{equation}
	and the loss function is:
	\begin{equation}
	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
	\end{equation}
	The training objective is to minimize $\mathcal{L}$.

@@

	\textbf{Tab.\ref{tab:result_RF}} describes the $ABC$ of two tasks in different data processing manner.
	\begin{table}[tbp]
		\centering  
		\begin{tabular}{lcc} 
			\hline
			Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
			$data-1$ & 0.4016    &0.8124   \\        
			$data-2$ &0.3985 &0.8261 \\        
			$data-3-ws10$  &0.7132 &0.8018 \\
			$data-3-ws20$ &0.6314 &0.7910 \\
			$data-3-ws50$ &0.5359  &0.7790 \\ \hline
		\end{tabular}
		\caption{Experiment results($ABC$) of random forest models. }
		\label{tab:result_RF}
	\end{table}
	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference in processing the data in different manners . They all achieve relatively good results, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality. However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality. It changes rapidly as time changes. And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model. Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves the largest $ABC$ compared with other processing manners. It considers only the recent data in a relatively short time slot. Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the recent previous \texttt{traceroute} data).
	\subsection{LSTM Model}

@@

	\begin{figure*} 	
		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-1-7030-lstm.pdf}
		%\vspace{-20pt}  
		\caption{Relative prediction errors for $R_r(t)$ of LSTM models with vector input.}
		\label{fig:lstm-task1-vector}
		%\vspace{-10pt}  
	\end{figure*}
	\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-3-7030-lstm.pdf}
	%\vspace{-20pt}  
	\caption{Relative prediction errors for  $avgRTT_P(t)$ of LSTM models with vector input.}
	\label{fig:lstm-task3-vector}
	%\vspace{-10pt}  
	\end{figure*}
	\begin{table}[t]
		\centering
		\begin{tabular}{lcc}
			\toprule
			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
			\midrule
			\textit{data-1}& 0.5374 & 0.7310 \\
			\textit{data-2}& 0.4956& 0.7039     \\
			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
			\textit{data-3-ws20}& 0.6513& 0.6901    \\
			\textit{data-3-ws50}& 0.5647& 0.7074  \\
			\bottomrule	
		\end{tabular}
		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
		\label{tab:lstm-vector}
	\end{table}

>>>>

	\subsection{LSTM Model}
	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling. More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input, i.e., $\mathbf{X}=(\mathbf{x_1}, \mathbf{x_2},...,\mathbf{x_{t-1}}, \mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
	\begin{equation}
	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
	\begin{equation}
	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
	\end{equation}
	and the loss function is:
	\begin{equation}
	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
	\end{equation}
	The training objective is to minimize $\mathcal{L}$.

@@

	\textbf{Tab.\ref{tab:result_RF}} describes the $ABC$ of two tasks in different data processing manner.
	\begin{table}[tbp]
		\centering  
		\begin{tabular}{lcc} 
			\hline
			Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
			\textit{data-1} & 0.4016    &0.8124   \\        
			\textit{data-2} &0.3985 &0.8261 \\        
			\textit{data-3-ws10}  &0.7132 &0.8018 \\
			\textit{data-3-ws20} &0.6314 &0.7910 \\
			\textit{data-3-ws50} &0.5359  &0.7790 \\ \hline
		\end{tabular}
		\caption{Experiment results($ABC$) of random forest models. }
		\label{tab:result_RF}
	\end{table}
	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference in processing the data in different manners . They all achieve relatively good results, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality. However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality. It changes rapidly as time changes. And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model. Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves the largest $ABC$ compared with other processing manners. It considers only the recent data in a relatively short time slot. Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the recent previous \texttt{traceroute} data).
	\subsection{LSTM Model}

@@

	\begin{figure*} 	
		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-lstm.pdf}
	\end{figure*} 
	\begin{figure*} 
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-1-7030-lstm.pdf}
		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-1-7030-lstm.pdf}
		%\vspace{-20pt}  
		\caption{Relative prediction errors for $R_r(t)$ of LSTM models with vector input.}
		\label{fig:lstm-task1-vector}
		%\vspace{-10pt}  
	\end{figure*}
	\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-lstm.pdf}
	\end{figure*} 
	\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-3-7030-lstm.pdf}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-3-7030-lstm.pdf}
	%\vspace{-20pt}  
	\caption{Relative prediction errors for  $avgRTT_P(t)$ of LSTM models with vector input.}
	\label{fig:lstm-task3-vector}
	%\vspace{-10pt}  
	\end{figure*}
	\begin{table}[t]
		\centering
		\begin{tabular}{lcc}
			\toprule
			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
			\midrule
			\textit{data-1}& 0.5374 & 0.7310 \\
			\textit{data-2}& 0.4956& 0.7039     \\
			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
			\textit{data-3-ws20}& 0.6513& 0.6901    \\
			\textit{data-3-ws50}& 0.5647& 0.7074  \\
			\bottomrule	
		\end{tabular}
		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
		\label{tab:lstm-vector}
	\end{table}
